---
title: "Introduction to sciRmdTheme: An R package for Styling Scientific Rmarkdown Documents"
author: "Obinna N. Obianom"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to sciRmdTheme: An R package for Styling Scientific Rmarkdown Documents}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r,echo=FALSE}
sciRmdTheme::set.theme(
  theme = "default",
  color = "purple",
  header.sticky=TRUE,
  header.image="https://coursewhiz.org/mainsite/logo.png",
  list.group.icon = "arrow",
  font.family = "Arial",
  font.color = "#333",
  header.color = "blue"
  )

```


The use of R Markdown and R Notebook for documenting processes, experiments and for writing reports has continued to grow in the last 5+ years. This is exciting, as more and more companies are also starting to adapt it for bookkeeping purposes. However, the available R markdown templates are not well-suited for professional reports and displays. Therefore, the purpose of the sciRmdTheme package is to provide more tools to help data analytists, scientists and writers in drafting professional R markdown pages.

## Installation and Library Attachment

The sciRmdTheme package is available on CRAN and can be installed as shown below

`install.packages(sciRmdTheme)`

Attach library 

`library(sciRmdTheme)`

## Use

The sciRmdTheme can be used within the R Markdown document using an R chunk as shown below


`sciRmdTheme::set.theme()`

or by using the available options. An example of how the available options can be used is show below

```{r eval=FALSE,echo=TRUE}
sciRmdTheme::set.theme(
  theme = "default",
  color = "purple",
  header.sticky=TRUE,
  header.image="https://coursewhiz.org/mainsite/logo.png",
  list.group.icon = "arrow",
  font.family = "Arial",
  font.color = "#333",
  header.color = "blue"
  )
```

## Features 

  - Simple user interface with adjusted letter sizing
  - Ability to use wide or narrow screen display width
  - Ability to set theme colors that a applied across the template
  - Ability to optimize the color of the title
  - Ability to add logo to the header section
  - Ability to use sticky or non-sticky headers
  - Image and table resizing options
  
## Examples and Demo Pages

View examples and demo pages at https://github.com/oobianom/sciRmdTheme
View other pages created by me at https://coursewhiz.org
