---
title: "Welcome to r2resize: In-text resizing for images and tables in Markdown and Quarto documents"
author: "Obinna N. Obianom"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Welcome to r2resize: In-text resizing for images and tables in Markdown and Quarto documents}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


## Easily add automatic resizing toolbar for all images and tables in Markdown, Rmarkdown and Quarto documents

### Installation and Library Attachment

The r2resize package is available on CRAN and can be installed as shown below

`install.packages(r2resize)`

Attach library 

`library(r2resize)`

### Use the easy resize functionality in Rmarkdown or Quarto

The r2resize can be used within the R Markdown or Quarto document using an R chunk as shown below


`r2resize::add.resizer()`

or by using the available options. An example of how the available options can be used is show below

```{r eval=TRUE,echo=TRUE}
r2resize::add.resizer(
  theme.color = "black",
  position = "top",
  font.size = "12px",
  font.color = "darkblue",
  tables = TRUE,
  images = TRUE,
  line.color = "orange",
  line.width = 150
)
```

### Use a lot of other cool functions such as the one below

```{r eval=TRUE,echo=TRUE}
library(r2symbols)
r2resize::emphasisCard("text1",symbol("ram","hippopotamus","alpha","beta",font.size=50), bg.color = "#f1f1f1")
```

### Quick demo: https://r2resize.obi.obianom.com/r2resize-package.gif


## More cool functions and examples and documentation

 + https://r2resize.obi.obianom.com
