---
title: "Welcome to r2resize: In-text resizing for images and tables in Markdown and Quarto documents"
author: "Obinna N. Obianom"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Welcome to r2resize: In-text resizing for images and tables in Markdown and Quarto documents}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


# Automatic resizing toolbar for images and tables in Markdown, Rmarkdown and Quarto documents

## Installation and Library Attachment

The r2resize package is available on CRAN and can be installed as shown below

`install.packages(r2resize)`

Attach library 

`library(r2resize)`

## Use

The r2resize can be used within the R Markdown document using an R chunk as shown below


`r2resize::add.resizer()`

or by using the available options. An example of how the available options can be used is show below

```{r eval=FALSE,echo=TRUE}
r2resize::add.resizer(
  theme.color = "black",
  position = "top",
  font.size = "12px",
  font.color = "gray",
  tables = TRUE,
  images = TRUE,
  line.color = "orange",
  line.width = 350
)
```

# Images Examples



Elit pellentesque habitant morbi tristique senectus et netus et malesuada. Amet massa vitae tortor condimentum lacinia quis vel eros. 

```{r pressure1, echo=FALSE}

plot(mtcars)


```


Ut ornare lectus sit amet est placerat in. Risus in hendrerit gravida rutrum quisque non tellus orci ac. Viverra justo nec ultrices dui sapien eget. Elit scelerisque mauris pellentesque pulvinar pellentesque. 

```{r pressure2, echo=FALSE}

plot(pressure)

plot(cars)

```


Imperdiet nulla malesuada pellentesque elit eget gravida. Turpis massa sed elementum tempus egestas.

```{r pressure3, echo=FALSE}

plot(pressure)

plot(mtcars)

plot(cars)

```

# Table Examples

Quis varius quam quisque id diam. Donec enim diam vulputate ut pharetra. Nunc aliquet bibendum enim facilisis gravida neque convallis a cras. Vitae tempus quam pellentesque nec nam aliquam sem et tortor. 


| Ex1      | Ex2      | Ex3      | Ex4      | Ex 5     |
|----------|----------|----------|----------|----------|
| 1        | 23       | 1        | 45       | 6 - 12   |
| 3        | 4        | 5        | NA       | 4 - 5.5  |
| 7        | 7        | 5        | 0        | 5 - 34   |


Libero id faucibus nisl tincidunt. Ultrices tincidunt arcu non sodales neque sodales ut etiam. Ut placerat orci nulla pellentesque dignissim enim sit amet. Tempus quam pellentesque nec nam. Egestas purus viverra accumsan in. Eu ultrices vitae auctor eu augue ut lectus. Leo integer malesuada nunc vel risus commodo.

## Table 1 and 2

| Column 1 | Column 2 | Column 3 | Column 4 | Column 5 |
|----------|----------|----------|----------|----------|
| 1        | 23       | 1        | 45       | 6 - 12   |
| 3        | 4        | 5        | NA       | 4 - 5.5  |
| 7        | 7        | 5        | 0        | 5 - 34   |

| head1 | head2 | head3 | head4 | head5 |
|-------|-------|-------|-------|-------|
| 1     | 23    | 1     | A     | AA    |
| 3     | 4     | 5     | B     | BB    |
| 7     | 7     | 5     | C     | CC    |
